{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-06-14 Notebook LaTEX/Momentum Accelerations/main.tex
>w< updates

    \subsection{Scenario I}
        In this scenario, we aim to recover the following variant of the accelerated gradient algorithm from 12.1 in Ryu's writing \cite{ryu_large-scale_2022}, it is: 
        \begin{align*}
            z_{t + 1} &= y_k + L^{-1}\nabla f(y_t), 
            \\
            y_{t + 1} &= z_{t + 1} + \frac{t - 1}{t + 2}\left(
                z_{k + 1} - z_k
            \right). 
        \end{align*}
        An equivalent form of the above is also provided by Ryu: 
        \begin{align*}
            z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
            \\
            x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t), 
            \\
            y_{t + 1} &= \left(
                1 - \frac{2}{t + 2} 
            \right)z_{t + 1} + 
            \left(
                \frac{1}{t + 2}
            \right)x_{t + 1}. 
        \end{align*}
        The base case requires cares since it's not unique, and depending on how the base case is define, there even more representations of it. 
        \begin{observation}
            Observe that the second equivalent form is an example of \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
            \par\noindent
            It is stated in Ryu's writing that the base case is $x_0 = y_0 = z_0$, 
            \textcolor{purple}{we think this is not the only options.} 
            We remind the reader that there is not an obvious choice of $t\in \mathbb Z$ such that $x_t = y_t = z_t$ where the above algorithm remains consistent for all $t \ge -1$. 
            The choice of base case presented in Ryu's writing is a choice and not a necessity. 
            We state that one of the base case scenario only requires knowing $y_1$.

@@

    \subsection{Scenario II}
        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983.

>>>>

    \subsection{Scenario I}
        In this scenario, we aim to recover the following variant of the accelerated gradient algorithm from 12.1 in Ryu's writing \cite{ryu_large-scale_2022}, it is: 
        \begin{align*}
            z_{t + 1} &= y_k + L^{-1}\nabla f(y_t), 
            \\
            y_{t + 1} &= z_{t + 1} + \frac{t - 1}{t + 2}\left(
                z_{k + 1} - z_k
            \right). 
        \end{align*}
        An equivalent form of the above is also provided by Ryu: 
        \begin{align*}
            z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
            \\
            x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t), 
            \\
            y_{t + 1} &= \left(
                1 - \frac{2}{t + 2} 
            \right)z_{t + 1} + 
            \left(
                \frac{1}{t + 2}
            \right)x_{t + 1}. 
        \end{align*}
        The base case requires cares since it's not unique, and depending on how the base case is define, there even more representations of it. 
        \begin{observation}
            Observe that the second equivalent form is an example of \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
            \par\noindent
            It is stated in Ryu's writing that the base case is $x_0 = y_0 = z_0$, 
            \textcolor{purple}{we think this is not the only options.} 
            We remind the reader that there is not an obvious choice of $t\in \mathbb Z$ such that $x_t = y_t = z_t$ where the above algorithm remains consistent for all $t \ge -1$. 
            The choice of base case presented in Ryu's writing is a choice and not a necessity. 
            We state that one of the base case scenario that only requires knowing $y_1$.

@@

            In the original writing by Ahn \cite[4.9]{ahn_understanding_2022}, they didn't list what exactly this algorithm is. Here we stated that it should be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}. 

    \subsection{Scenario II}
        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
        We will discuss how other choices of $\tilde \eta_{t +1}$ results in other varients of the Accelerated gradient such as the variants proposed by Chambolle \cite{chambolle_convergence_2015}.
